### 2019-10-22 README.Rmd
use .bib file in README

---
output: github_document
---

@@

<div id="refs" class="references">

<div id="ref-Brenning2012">

**Brenning**, A, 2012. “Spatial cross-validation and bootstrap for the assessment of
prediction rules in remote sensing: The R Package sperrorest.” In *2012
IEEE International Geoscience and Remote Sensing Symposium*, 5372–5.
<https://doi.org/10.1109/IGARSS.2012.6352393>.

</div>

<div id="ref-Valavi2019">

**Valavi** R, Elith J, Lahoz-Monfort JJ, Guillera-Arroita G. blockCV: An R package for generating spatially or environmentally separated folds for k-fold cross-validation of species distribution models. Methods Ecol Evol. 2019; 10:225–232. doi.org/10.1111/2041-210X.13107

</div>

</div>

>>>>

---
output: github_document
bibliography: inst/references.bib
nocite: | 
  @brenning2012, @valavi2018
---

@@
